% !TEX program = pdflatex
\documentclass[9pt,a4paper]{article}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\geometry{top=1.2cm,bottom=1.0cm,left=1.3cm,right=1.3cm}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{tcolorbox}
\tcbuselibrary{skins}

\setlist{nosep,leftmargin=1.0em,topsep=0pt,partopsep=0pt}
\pagestyle{empty}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{12pt}

\begin{document}

\begin{center}
{\Large\bfseries BH Thermodynamics Programme: Overview of the Six-Paper Research Programme}\\[2pt]
{\small Noriaki Kihara\enspace WF System Co., Ltd.\enspace Osaka University, Faculty of Engineering Science (B.Eng.)\enspace ORCID: \href{https://orcid.org/0009-0004-6753-4020}{0009-0004-6753-4020}}
\end{center}

\vspace{-1pt}
\hrule height 0.7pt
\vspace{4pt}

\begin{tcolorbox}[colback=gray!7,colframe=gray!55,boxrule=0.4pt,arc=2pt,left=4pt,right=4pt,top=2pt,bottom=2pt]
{\small
\textbf{Claim 1: Asymptotic constant $c = 8/(3\pi)$ for unit-cube packing in a 4D ball.}\enspace
For a four-dimensional ball of radius $R = 2k+1$, the count $N(k)$ of integer-centred unit cubes contained in it gives a volume deficit $\Delta(R) = V_4(R) - N(k)$ whose leading constant is derived in closed form by inclusion--exclusion: $c = 8/(3\pi) \approx 0.84883$. Numerical verification agrees to within 0.024\%. {\scriptsize(Paper 3)}\\[2pt]
\textbf{Claim 2: Exact agreement with 4+1-dimensional Tangherlini black hole thermodynamics.}\enspace
Self-consistent determination of the central-projection metric yields $R \propto M^{1/2}$, Hawking temperature $T_H \propto M^{-1/2}$, lifetime $\tau \propto M^{3/2}$, and evaporation rate $dM/dt \propto -M^{-1/2}$. The ratio with the Bekenstein--Hawking entropy is $\Delta(R)/S_{BH} \to 32/(3\pi) \approx 3.40$. {\scriptsize(Papers 4--5)}\\[2pt]
\textbf{Claim 3: Independent path without holographic assumptions.}\enspace
The programme does \textbf{not} assume the 't~Hooft--Susskind holographic principle, the Maldacena AdS/CFT correspondence, or any specific quantum-gravity programme (LQG/CDT/string theory). It derives the above results from minimal geometric and combinatorial assumptions only --- central projection and Planck-scale discreteness. Zero self-citation. {\scriptsize(Papers 1--6)}}
\end{tcolorbox}

\vspace{2pt}

\begin{multicols}{2}
\small

\textbf{Paper 1: Overview and Hypotheses}\enspace
From premises A (entropy is geometric), B (evaporation is horizon-local), and C (spacetime may be discrete at the Planck scale), two conditional propositions are extracted: Hypothesis 1 (Projection) and Hypothesis 2 (Discrete Drift).

\smallskip
\textbf{Paper 2: Mathematical Foundations of Central Projection}\enspace
Gnomonic projection from $S^4(R) \subset \mathbb{R}^5$ to a four-dimensional tangent hyperplane. The induced metric $g_{\mu\nu} = (R^2/\ell^2)(\delta_{\mu\nu} - x_\mu x_\nu/\ell^2)$ satisfies $G_{\mu\nu} + (3/R^2)g_{\mu\nu} = 0$, becomes de Sitter under Lorentzian continuation, and Schwarzschild--de Sitter with a mass parameter.

\smallskip
\textbf{Paper 3: Mathematical Foundations of Discreteness}\enspace
Packing condition $\sum (|c_i|+1/2)^2 \le R^2$. Exact computation of $N(k)$ for $k = 0..60$ (with $N(60) = 1{,}028{,}515{,}513$). Asymptotic expansion $\Delta(R) = (16\pi/3)R^3 - 6\pi R^2 + O(R)$. Connection to the Lagrange--Jacobi four-square representation count $r_4(N) = 8\sigma(N)$.

\smallskip
\textbf{Papers 4 and 5: Physical Connection and Dynamics}\enspace
Constant ratio $32/(3\pi)$ between $\Delta(R)$ and the 4+1 Bekenstein--Hawking entropy. From a Friedmann-like relation $E_{\mathrm{total}} \propto R^2$, all Tangherlini scaling laws are recovered.

\smallskip
\textbf{Paper 6: Synthesis and Open Problem}\enspace
The principal open problem --- how the 4+1-dimensional results reduce to observed 3+1-dimensional black hole physics --- is precisely formulated. Three candidate mechanisms: KK compactification, Randall--Sundrum/ADD brane localization, dS-CFT-style holographic projection.

\vspace{6pt}
\textbf{DOIs of the Six Papers}

\vspace{1pt}
{\footnotesize
\begin{tabular}{@{}ll@{}}
Paper 1 (Overview)  & \href{https://doi.org/10.5281/zenodo.19837588}{10.5281/zenodo.19837588} \\
Paper 2 (Projection) & \href{https://doi.org/10.5281/zenodo.19837590}{10.5281/zenodo.19837590} \\
Paper 3 (Packing) & \href{https://doi.org/10.5281/zenodo.19837592}{10.5281/zenodo.19837592} \\
Paper 4 (Entropy) & \href{https://doi.org/10.5281/zenodo.19837594}{10.5281/zenodo.19837594} \\
Paper 5 (Dynamics) & \href{https://doi.org/10.5281/zenodo.19837596}{10.5281/zenodo.19837596} \\
Paper 6 (Synthesis) & \href{https://doi.org/10.5281/zenodo.19837598}{10.5281/zenodo.19837598} \\
\end{tabular}
}

\columnbreak

\textbf{Correspondence with 4+1 Tangherlini}

\vspace{1pt}
\begin{center}
\footnotesize
\begin{tabular}{@{}lll@{}}
\toprule
Quantity & Central-projection & 4+1 Tangherlini \\
\midrule
Mass--radius & $R \propto M^{1/2}$ & $r_h \propto M^{1/2}$ \\
Hawking temperature & $T_H \propto M^{-1/2}$ & identical \\
Lifetime & $\tau \propto M^{3/2}$ & identical \\
Entropy scaling & $\Delta(R) \propto R^3$ & $S_{BH} \propto R^3$ \\
Ratio & \multicolumn{2}{l}{$\Delta/S_{BH} \to 32/(3\pi)$} \\
\bottomrule
\end{tabular}
\end{center}

\vspace{6pt}
\textbf{What This Research Does \emph{Not} Claim}

\vspace{1pt}
\begin{itemize}[topsep=1pt]
\item That physical spacetime is 4+1-dimensional
\item That higher-dimensional spacetime physically exists
\item A first-principles derivation of the Bekenstein--Hawking entropy
\item A replacement of holographic or quantum-gravity programmes
\end{itemize}

\vspace{1pt}
{\footnotesize The ``discrepancy'' in the evaporation-rate exponent originally flagged in the programme outline is, in fact, a confusion between 3+1 and 4+1 conventions; in 4+1 dimensions the agreement is exact. The genuine open problem is the 4+1 $\to$ 3+1 reduction mechanism.}

\end{multicols}

\vspace{0pt}
\hrule height 0.4pt
\vspace{3pt}

\begin{center}
\begin{minipage}[c]{14cm}
{\footnotesize\textbf{Zenn article}\enspace \url{https://zenn.dev/noriaki_kihara/articles/bh-thermodynamics-projection}}\\[1pt]
{\footnotesize\textbf{Note (Japanese)}\enspace \url{https://note.com/kiharanoriaki/n/n4524006ef175}}\\[1pt]
{\footnotesize\textbf{Note (English)}\enspace \url{https://note.com/kiharanoriaki/n/n916eac778c1c}}\\[1pt]
{\footnotesize\textbf{Source code (GitHub)}\enspace \url{https://github.com/WurabeSeiji/ai-chat-logs-open/tree/main/BH熱力学プログラム}}\\[1pt]
{\scriptsize All papers are available on Zenodo as PDF, LaTeX, and Markdown (Japanese/English bilingual, CC BY 4.0).}
\end{minipage}
\end{center}

\end{document}
