\documentclass[a4paper,11pt]{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{longtable,booktabs,array,calc}
\usepackage{hyperref}
\usepackage[margin=25mm]{geometry}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{observation}[theorem]{Observation}

\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\newcounter{none}

\begin{document}

\section{The sine-Gordon Equation --- Foundations of Topological Soliton
Theory}\label{the-sine-gordon-equation-foundations-of-topological-soliton-theory}

\subsection{--- Classification of Topological Solutions and Collision
Properties in Nonlinear Wave Equations
---}\label{classification-of-topological-solutions-and-collision-properties-in-nonlinear-wave-equations}

\textbf{Author:} Noriaki Kihara (WF System Co., Ltd.)

\textbf{Date:} April 2026

\textbf{DOI:}
\href{https://doi.org/10.5281/zenodo.19650966}{10.5281/zenodo.19650966}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{0. Purpose}\label{purpose}

This paper surveys the mathematical structure of the \textbf{sine-Gordon
equation}, one of the fundamental nonlinear wave equations. The
sine-Gordon equation admits topological solitons as solutions and is
widely applied in particle physics, condensed-matter physics, and field
theory.

We review the definition of the sine-Gordon equation, the classification
of its solutions (kink, antikink, breather), phase shifts upon
collision, and physical applications, tracing back to the original
literature. Furthermore, we prove that soliton solutions are exactly
characterized by a finite number of parameters, and that all structural
properties of solitons are preserved in the rectangular-wave limit
\(\sigma \to 0\). In addition, we explicitly identify the limitations of
the sine-Gordon theory (§9.8) and present an alternative model that
overcomes them: a formulation based on wave equations for perfectly
elastic collisions at arbitrary phases in a perfect fluid with different
specific gravities (§11).

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{1. Definition of the sine-Gordon
Equation}\label{definition-of-the-sine-gordon-equation}

\subsubsection{1.1 The Equation}\label{the-equation}

The 1+1-dimensional sine-Gordon equation is defined as follows {[}1,
2{]}.

\[\frac{\partial^2 \phi}{\partial t^2} - \frac{\partial^2 \phi}{\partial x^2} + \sin(\phi) = 0\]

Here \(\phi = \phi(x, t)\) is a scalar field (phase field), \(x\) is the
spatial coordinate, and \(t\) is the time coordinate.

Natural units (\(c = 1\), \(m = 1\)) are employed. Restoring the general
mass parameter \(m\) and the speed of light \(c\),

\[\frac{1}{c^2}\frac{\partial^2 \phi}{\partial t^2} - \frac{\partial^2 \phi}{\partial x^2} + \frac{m^2 c^2}{\hbar^2}\sin(\phi) = 0\]

\subsubsection{1.2 Origin of the Name}\label{origin-of-the-name}

The name ``sine-Gordon equation'' derives from its analogy with the
Klein-Gordon equation

\[\frac{\partial^2 \phi}{\partial t^2} - \frac{\partial^2 \phi}{\partial x^2} + m^2 \phi = 0\]

in which the linear term \(m^2 \phi\) is replaced by the nonlinear term
\(\sin(\phi)\). The name is a portmanteau of ``sine'' and ``Gordon,''
introduced by Rubinstein {[}3{]}.

\subsubsection{1.3 Lagrangian Density}\label{lagrangian-density}

The sine-Gordon equation is derived from the following Lagrangian
density {[}4{]}.

\[\mathcal{L} = \frac{1}{2}\left(\frac{\partial \phi}{\partial t}\right)^2 - \frac{1}{2}\left(\frac{\partial \phi}{\partial x}\right)^2 - (1 - \cos\phi)\]

The potential \(V(\phi) = 1 - \cos\phi\) attains its minimum value of 0
at \(\phi = 2n\pi\) (\(n \in \mathbb{Z}\)). The existence of these
infinitely many degenerate vacua is the origin of topological solitons.

\subsubsection{1.4 Historical Background}\label{historical-background}

The sine-Gordon equation was independently introduced in the following
contexts.

\begin{itemize}
\tightlist
\item
  \textbf{Crystal dislocation theory} (1939): Frenkel and Kontorova
  introduced it as a model describing the motion of dislocations in
  crystal lattices {[}1{]}.
\item
  \textbf{Differential geometry} (19th century): Bour {[}5{]} and
  Enneper {[}6{]} derived an isomorphic equation in the theory of
  surfaces with constant negative curvature (pseudospheres). Bianchi
  {[}7{]} studied the Bäcklund transformation of this equation.
\item
  \textbf{Particle physics} (1960s): Skyrme used a sine-Gordon-type
  equation as a nonlinear field theory model for baryons {[}8{]}.
  Perring and Skyrme carried out the first numerical computation of
  kink-antikink collisions {[}9{]}.
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{2. Classification of
Solutions}\label{classification-of-solutions}

\subsubsection{\texorpdfstring{2.1 Kink Solution (Winding Number
\(+1\))}{2.1 Kink Solution (Winding Number +1)}}\label{kink-solution-winding-number-1}

The kink solution is a localized wave in which \(\phi\) smoothly
transitions from \(0\) to \(2\pi\) {[}2, 9{]}.

\[\phi_K(x, t) = 4\arctan\left(\exp\left(\frac{x - vt}{\sqrt{1 - v^2}}\right)\right)\]

Here \(v\) (\(|v| < 1\)) is the velocity of the kink.

\textbf{Properties:}

\begin{itemize}
\tightlist
\item
  \(\phi \to 0\) as \(x \to -\infty\), \(\phi \to 2\pi\) as
  \(x \to +\infty\)
\item
  The phase increases by \(2\pi\) --- \textbf{winding number
  (topological charge)} \(N = +1\)
\item
  The denominator \(\sqrt{1 - v^2}\) is the Lorentz factor, ensuring
  special-relativistic covariance
\item
  Rest energy \(E_0 = 8m\) (in natural units \(E_0 = 8\))
\end{itemize}

\subsubsection{\texorpdfstring{2.2 Antikink Solution (Winding Number
\(-1\))}{2.2 Antikink Solution (Winding Number -1)}}\label{antikink-solution-winding-number--1}

The antikink solution is a localized wave in which \(\phi\) transitions
from \(2\pi\) to \(0\) {[}2{]}.

\[\phi_{\bar{K}}(x, t) = 4\arctan\left(\exp\left(-\frac{x - vt}{\sqrt{1 - v^2}}\right)\right)\]

\textbf{Properties:}

\begin{itemize}
\tightlist
\item
  \(\phi \to 2\pi\) as \(x \to -\infty\), \(\phi \to 0\) as
  \(x \to +\infty\)
\item
  The phase decreases by \(2\pi\) --- \textbf{winding number} \(N = -1\)
\item
  Same mass and velocity characteristics as the kink
\end{itemize}

\subsubsection{2.3 Definition and Conservation of Winding
Number}\label{definition-and-conservation-of-winding-number}

\textbf{Definition 2.1.} The \textbf{winding number} (topological
charge) of a field configuration \(\phi(x, t)\) is defined as {[}4,
10{]}:

\[N = \frac{1}{2\pi}\int_{-\infty}^{+\infty} \frac{\partial \phi}{\partial x}\,dx = \frac{\phi(+\infty) - \phi(-\infty)}{2\pi}\]

\textbf{Proposition 2.1 (Conservation of winding number).} Under the
time evolution of the sine-Gordon equation, the winding number \(N\) is
conserved.

\emph{Proof.} The boundary values \(\phi(\pm\infty)\) are fixed at
vacuum values (\(2n\pi\)) and cannot change by an integer multiple of
\(2\pi\) under continuous time evolution. Therefore \(N\) is conserved
as a time-independent integer. \(\square\)

This conservation law guarantees the ``particle nature'' of solitons ---
creation and annihilation are possible only in pairs (kink + antikink).

\subsubsection{2.4 Breather Solution (Bound Oscillatory
State)}\label{breather-solution-bound-oscillatory-state}

A breather is an oscillatory solution in which a kink and an antikink
are bound together, carrying winding number \(N = 0\) {[}2, 11{]}.

\[\phi_B(x, t) = 4\arctan\left(\frac{\sqrt{1 - \omega^2}\;\cos(\omega t)}{\omega\;\cosh\left(\sqrt{1 - \omega^2}\;x\right)}\right)\]

Here \(\omega\) (\(0 < \omega < 1\)) is the internal oscillation
frequency of the breather.

\textbf{Properties:}

\begin{itemize}
\tightlist
\item
  A localized oscillatory solution that decays exponentially in space
\item
  A smaller \(\omega\) yields a broader spatial extent of the breather
\item
  Rest mass of the breather: \(M_B = 16\sqrt{1 - \omega^2}\)
\item
  In the limit \(\omega \to 0\), the breather mass approaches that of a
  kink-antikink pair (\(2 \times 8 = 16\))
\item
  In the limit \(\omega \to 1\), the breather mass approaches \(0\),
  transitioning to linear small oscillations (mesons)
\end{itemize}

\subsubsection{2.5 Summary of Solution
Classification}\label{summary-of-solution-classification}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2381}}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2857}}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1905}}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1429}}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1429}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Solution type
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Winding number \(N\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Localization
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Oscillation
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Mass
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Kink & \(+1\) & Localized & None & \(8\) \\
Antikink & \(-1\) & Localized & None & \(8\) \\
Breather & \(0\) & Localized & Yes & \(16\sqrt{1-\omega^2}\) \\
Meson (linear wave) & \(0\) & Non-localized & Yes & \(\geq 2\)
(threshold) \\
\end{longtable}
}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{3. Soliton Collisions and Phase
Shifts}\label{soliton-collisions-and-phase-shifts}

\subsubsection{3.1 Kink-Kink Collision}\label{kink-kink-collision}

The collision of two kinks with the same sign (\(N = +1\) and
\(N = +1\)) is repulsive, and the two-body solution is given by {[}2,
12{]}:

\[\phi_{KK}(x, t) = 4\arctan\left(\frac{v\,\sinh\left(\frac{x}{\sqrt{1-v^2}}\right)}{\cosh\left(\frac{vt}{\sqrt{1-v^2}}\right)}\right)\]

After the collision, the two kinks separate again, perfectly preserving
their shape. However, compared to the case without collision, each
kink's position is displaced by a \textbf{phase shift} \(\Delta x\).

\[\Delta x = \frac{\sqrt{1 - v^2}}{v}\ln(v^2)\]

\subsubsection{3.2 Kink-Antikink
Collision}\label{kink-antikink-collision}

The collision of a kink and an antikink with opposite signs (\(N = +1\)
and \(N = -1\)) is attractive, and the two-body solution is given by
{[}2, 9, 12{]}:

\[\phi_{K\bar{K}}(x, t) = 4\arctan\left(\frac{v^{-1}\,\cosh\left(\frac{vt}{\sqrt{1-v^2}}\right)}{\sinh\left(\frac{x}{\sqrt{1-v^2}}\right)}\right)\]

\textbf{Properties:}

\begin{itemize}
\tightlist
\item
  With sufficient energy, the kink and antikink pass through each other
  and separate again (perfectly elastic collision: velocities and shapes
  are identical to those before the collision, with only a phase shift)
\item
  With insufficient energy, they form a breather (bound state) that
  oscillates perpetually without decay
\end{itemize}

\textbf{Note:} In the classical fully integrable sine-Gordon equation,
annihilation of a kink-antikink pair into radiation waves (mesons) does
not occur. This phenomenon arises only in quantum effects or in systems
where integrability is broken (perturbations, discretization, higher
dimensions).

\subsubsection{3.3 Physical Meaning of the Phase
Shift}\label{physical-meaning-of-the-phase-shift}

\textbf{Proposition 3.1 (Shape preservation and phase shift).} In
soliton collisions of the sine-Gordon equation,

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The \textbf{shape} of each soliton after the collision is identical to
  that before the collision.
\item
  The \textbf{position} of each soliton after the collision is displaced
  by a phase shift \(\Delta x\) compared to the case without collision.
\item
  The total winding number is conserved before and after the collision.
\end{enumerate}

\emph{Proof.} The sine-Gordon equation can be solved exactly by the
inverse scattering method {[}12{]}, and multi-soliton solutions
asymptotically separate into a superposition of individual solitons. The
asymptotic shape of each soliton is identical to that before the
collision, but a phase shift is added. The winding number is conserved
as a topological invariant. \(\square\)

This property is critically important for the theory. The \textbf{type}
(winding number = orientation structure) of a soliton (= particle) is
invariant under interactions, and only the \textbf{position} (phase)
changes.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{4. Complete Integrability and the Inverse Scattering
Method}\label{complete-integrability-and-the-inverse-scattering-method}

\subsubsection{4.1 Lax Pair}\label{lax-pair}

The sine-Gordon equation is a \textbf{completely integrable system} and
possesses a Lax pair {[}12, 13{]}.

In light-cone coordinates \(u = \frac{1}{2}(x - t)\),
\(v = \frac{1}{2}(x + t)\), the equation becomes

\[\frac{\partial^2 \phi}{\partial u\,\partial v} = \sin\phi\]

This equation is expressed as the compatibility condition of the
following Lax pair.

\[\Psi_u = U\Psi, \quad \Psi_v = V\Psi\]

Here \(U\) and \(V\) are \(2 \times 2\) matrices depending on the
spectral parameter \(\lambda\) {[}12{]}.

\subsubsection{4.2 Infinitely Many Conserved
Quantities}\label{infinitely-many-conserved-quantities}

As a consequence of complete integrability, the sine-Gordon equation
possesses infinitely many independent conserved quantities {[}12, 14{]}.
The first three are:

\begin{itemize}
\item
  \textbf{Energy:}
  \[E = \int_{-\infty}^{+\infty}\left[\frac{1}{2}\left(\frac{\partial\phi}{\partial t}\right)^2 + \frac{1}{2}\left(\frac{\partial\phi}{\partial x}\right)^2 + (1-\cos\phi)\right]dx\]
\item
  \textbf{Momentum:}
  \[P = -\int_{-\infty}^{+\infty}\frac{\partial\phi}{\partial t}\frac{\partial\phi}{\partial x}\,dx\]
\item
  \textbf{Winding number:}
  \[N = \frac{1}{2\pi}\int_{-\infty}^{+\infty}\frac{\partial\phi}{\partial x}\,dx\]
\end{itemize}

\subsubsection{4.3 Bäcklund
Transformation}\label{buxe4cklund-transformation}

The sine-Gordon equation admits a Bäcklund transformation, which
generates new solutions from known ones {[}7, 15{]}.

Given a known solution \(\phi_0\), the solution \(\phi_1\) of the
following system of equations is also a solution of the sine-Gordon
equation.

\[\frac{\partial}{\partial u}\left(\frac{\phi_1 + \phi_0}{2}\right) = a\,\sin\left(\frac{\phi_1 - \phi_0}{2}\right)\]

\[\frac{\partial}{\partial v}\left(\frac{\phi_1 - \phi_0}{2}\right) = \frac{1}{a}\sin\left(\frac{\phi_1 + \phi_0}{2}\right)\]

Here \(a\) is the parameter of the Bäcklund transformation. Starting
from the vacuum solution \(\phi_0 = 0\), a single Bäcklund
transformation yields the kink solution, and two transformations yield
the kink-kink solution or the breather solution {[}15{]}.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{5. Extension to Higher
Dimensions}\label{extension-to-higher-dimensions}

\subsubsection{5.1 2+1 and 3+1 Dimensions}\label{and-31-dimensions}

The direct extension of the sine-Gordon equation to higher dimensions is

\[\frac{\partial^2\phi}{\partial t^2} - \nabla^2\phi + \sin(\phi) = 0\]

However, in 2+1 dimensions and above, this equation is no longer
completely integrable {[}16{]}. Furthermore, by Derrick's theorem
{[}17{]}, no stable localized solutions (solitons) composed solely of
scalar fields exist in 3+1 dimensions.

\subsubsection{5.2 Methods of
Stabilization}\label{methods-of-stabilization}

The following methods are known for obtaining stable solitons in higher
dimensions {[}10, 18{]}.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Skyrme model}: Adding higher-order derivative terms (Skyrme
  term) {[}8, 18{]}.
\item
  \textbf{Coupling with gauge fields}: Coupling scalar fields to gauge
  fields.
\item
  \textbf{Topological stabilization}: When the field carries a
  nontrivial topological charge, energy minimization prohibits the
  collapse of the soliton {[}10{]}.
\end{enumerate}

\subsubsection{5.3 Stabilization on Closed
Spaces}\label{stabilization-on-closed-spaces}

When treating solitons on higher-dimensional spaces, a mechanism for
circumventing Derrick's theorem is required. On a closed curve \(S^1\)
with circumference \(L\), the premises of Derrick's theorem (asymptotic
conditions on infinite space) are violated, and stable soliton solutions
can exist {[}10{]}.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{6. Physical Applications}\label{physical-applications}

\subsubsection{6.1 Condensed-Matter
Physics}\label{condensed-matter-physics}

\begin{itemize}
\tightlist
\item
  \textbf{Josephson junctions}: The motion of magnetic flux quanta
  across tunnel junctions between superconductors is described by the
  sine-Gordon equation {[}19{]}. Kinks correspond to magnetic flux
  quanta (fluxons).
\item
  \textbf{Crystal dislocations}: Dislocations in crystal lattices in the
  Frenkel-Kontorova model correspond to kink solutions {[}1{]}.
\end{itemize}

\subsubsection{6.2 Particle Physics}\label{particle-physics}

\begin{itemize}
\tightlist
\item
  \textbf{Skyrme model}: Baryons are described as topological solitons
  (Skyrmions) {[}8, 18{]}. The baryon number corresponds to the
  topological charge.
\item
  \textbf{Equivalence of the quantum sine-Gordon model and the massive
  Thirring model}: Coleman {[}20{]} and Mandelstam {[}21{]} showed that
  the quantum theory of the sine-Gordon model is equivalent to the
  massive Thirring model (a fermionic field theory). The
  \textbf{boson-fermion correspondence}, in which bosonic solitons
  correspond to fermions, is one of the most remarkable results of
  1+1-dimensional field theory.
\end{itemize}

\subsubsection{6.3 Differential Geometry}\label{differential-geometry}

\begin{itemize}
\tightlist
\item
  \textbf{Pseudospheres}: The compatibility conditions of the first and
  second fundamental forms of surfaces with constant negative curvature
  (\(K = -1\)) reduce to the sine-Gordon equation {[}5, 6{]}. Kink
  solutions correspond to geodesics on pseudospheres.
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{7. Implications for Physical
Interpretation}\label{implications-for-physical-interpretation}

\subsubsection{7.1 Summary of Particle-like Properties of
Solitons}\label{summary-of-particle-like-properties-of-solitons}

Soliton solutions of the sine-Gordon equation naturally possess the
following particle-like properties.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.4194}}
  >{\centering\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.5806}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Soliton property
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Correspondence to particles
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Winding number \(N = \pm 1\) & Particle / antiparticle \\
Conservation of winding number & Conservation of particle number \\
Shape preservation in collisions & Identity of particles \\
Phase shift (position change after collision) & Scattering through
interaction \\
Lorentz covariance & Special-relativistic structure \\
Breather (\(N = 0\) bound state) & Meson-like bound state \\
Periodicity of potential (\(2\pi\)) & Discreteness of phase \\
Boson-fermion correspondence {[}20, 21{]} & Spin-statistics \\
\end{longtable}
}

\subsubsection{7.2 Significance of the Rectangular-Wave
Description}\label{significance-of-the-rectangular-wave-description}

As shown in §8--§9, all of these particle-like properties are preserved
in the rectangular-wave limit \(\sigma \to 0\). This means that the
essential information of solitons is not contained in the smooth shape
of the continuous field but is concentrated in the topological and
scattering discrete structures.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{8. Finite-Parameter Representation of
Solitons}\label{finite-parameter-representation-of-solitons}

\subsubsection{8.1 Motivation: From Continuous Fields to Finite
Parameters}\label{motivation-from-continuous-fields-to-finite-parameters}

Solutions of the sine-Gordon equation are defined as continuous fields
\(\phi(x, t)\), but soliton solutions, by virtue of their localization,
are \textbf{completely characterized by a finite number of parameters}.
This is no coincidence. Solitons are \textbf{finite-mode solutions} in
the mode decomposition of nonlinear fields, restricted to a
finite-dimensional invariant manifold (moduli space) within an
infinite-dimensional field theory {[}10, 22{]}.

In this section, we give a formulation describing soliton solutions of
the sine-Gordon equation with a finite number of parameters, making
explicit how solutions of the continuous wave equation are reduced to a
small number of discrete pieces of information.

\subsubsection{8.2 Five-Parameter Representation of the
Kink}\label{five-parameter-representation-of-the-kink}

We restate the kink solution from §2.1.

\[\phi_K(x, t) = 4\arctan\left(\exp\left(\frac{x - x_0 - vt}{\ell}\right)\right)\]

Here \(\ell = \sqrt{1 - v^2}\) is the width parameter of the kink. This
solution is \textbf{completely} determined by the following five
parameters.

\textbf{Definition 8.1 (Soliton parameters).} The five parameters
characterizing a 1+1-dimensional sine-Gordon kink are defined as
follows.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Symbol
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Definition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Range
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\(N\) & Winding number & Topological charge \(\pm 1\) &
\(\{-1, +1\}\) \\
\(A\) & Maximum wave height & Total change in \(\phi\) \(= 2\pi |N|\) &
\(2\pi\) (fixed) \\
\(\theta_0\) & Central phase & Spatial phase of soliton center
\(= 2\pi x_0 / L\) & \([0, 2\pi)\) \\
\(\alpha\) & Translational phase & Phase-angle representation of
velocity \(v = \sin\alpha\) & \((-\pi/2, \pi/2)\) \\
\(\sigma\) & Spread phase & Phase-angle representation of width
\(\ell = \cos\alpha\) & \((0, 1]\) \\
\end{longtable}
}

\textbf{Proposition 8.1 (Completeness of parameters).} A single kink
(antikink) solution of the sine-Gordon equation is uniquely determined
by the above five parameters \((N, A, \theta_0, \alpha, \sigma)\).
Conversely, the five parameters are uniquely read off from any kink
solution.

\emph{Proof.} The general form of the kink solution is
\(\phi = 4\arctan(\exp(\pm(x - x_0 - vt)/\sqrt{1-v^2}))\), where the
sign \(\pm\) determines \(N\), the displacement \(x_0\) determines
\(\theta_0\), and the velocity \(v\) determines \(\alpha\). \(A = 2\pi\)
is fixed by \(|N| = 1\), and \(\sigma = \cos\alpha\) is determined
subordinately from \(\alpha\). The free parameters are three:
\((N, \theta_0, \alpha)\), with \(A\) and \(\sigma\) derived from these.
\(\square\)

\textbf{Note.} The free parameters are effectively three
(\(N, \theta_0, \alpha\)), but we adopt the five-parameter
representation for clarity of physical interpretation. \(A\) is
determined from the winding number, and \(\sigma\) from the
translational phase --- both are dependent parameters.

\subsubsection{8.3 Relation Between Translational Phase and Spread
Phase}\label{relation-between-translational-phase-and-spread-phase}

The following identity holds between the translational phase \(\alpha\)
and the spread phase \(\sigma\).

\[\sin^2\alpha + \sigma^2 = v^2 + \ell^2 = 1\]

That is, \((\sin\alpha, \sigma) = (v, \ell)\) is a point on the unit
circle.

\textbf{Physical interpretation:}

\begin{itemize}
\tightlist
\item
  \(\alpha = 0\) (at rest): \(\sigma = 1\) --- the soliton has maximum
  width
\item
  \(\alpha \to \pm\pi/2\) (speed of light): \(\sigma \to 0\) --- the
  soliton width contracts to zero (Lorentz contraction)
\item
  Faster motion yields narrower spatial extent --- \textbf{motion and
  shape are unified by a single phase angle \(\alpha\)}
\end{itemize}

\subsubsection{8.4 Six-Parameter Representation of the
Breather}\label{six-parameter-representation-of-the-breather}

The breather solution of §2.4 requires the internal oscillation
frequency \(\omega\) in addition to the five kink parameters.

\textbf{Definition 8.2 (Breather parameters).}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Symbol
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Definition
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Range
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\(N\) & Winding number & \(0\) (kink-antikink bound) & \(\{0\}\)
(fixed) \\
\(A\) & Maximum wave height & \(4\arctan(\sqrt{1-\omega^2}/\omega)\) &
\((0, \pi)\) \\
\(\theta_0\) & Central phase & Spatial phase of breather center &
\([0, 2\pi)\) \\
\(\alpha\) & Translational phase & Bulk motion \(v = \sin\alpha\) &
\((-\pi/2, \pi/2)\) \\
\(\sigma\) & Spread phase & \(1/\sqrt{1-\omega^2}\) & \([1, \infty)\) \\
\(\omega\) & Internal phase velocity & Angular frequency of internal
oscillation & \((0, 1)\) \\
\end{longtable}
}

The breather has \(N = 0\) but possesses an additional degree of freedom
in the internal oscillation \(\omega\).

\subsubsection{8.5 Parameter Representation of Multi-Soliton
States}\label{parameter-representation-of-multi-soliton-states}

A multi-body state consisting of \(n\) solitons is represented as a
collection of parameters for each soliton {[}10, 12{]}.

\textbf{Definition 8.3 (\(n\)-soliton state).} A state consisting of
\(n\) solitons is defined by the following parameter set.

\[\mathcal{S}_n = \{(N_i, A_i, \theta_{0,i}, \alpha_i, \sigma_i)\}_{i=1}^{n}\]

\textbf{Proposition 8.2 (Asymptotic completeness).} A field
configuration \(\phi(x, t)\) consisting of \(n\) well-separated solitons
is asymptotically completely determined by the parameter set
\(\mathcal{S}_n\). In regions where the overlap between solitons is
negligible,

\[\phi(x, t) \approx \sum_{i=1}^{n} \phi_i(x, t; N_i, \theta_{0,i}, \alpha_i)\]

holds, where \(\phi_i\) is the single-soliton solution for each soliton.

\emph{Proof.} By the inverse scattering method {[}12{]}, the
\(n\)-soliton solution is completely determined by \(n\) scattering data
(eigenvalues and norming constants). In the asymptotic region, the
scattering data correspond one-to-one with the above parameters.
\(\square\)

\subsubsection{8.6 Description of Collisions in Parameter
Space}\label{description-of-collisions-in-parameter-space}

The soliton collisions of §3 can be described as mappings in parameter
space.

\textbf{Proposition 8.3 (Collision map).} The collision of two solitons
\(\mathcal{S}_1 = (N_1, \theta_{0,1}, \alpha_1)\) and
\(\mathcal{S}_2 = (N_2, \theta_{0,2}, \alpha_2)\) is described as the
following parameter transformation.

\[\mathcal{S}_1' = (N_1,\; \theta_{0,1} + \Delta\theta_1,\; \alpha_1)\]
\[\mathcal{S}_2' = (N_2,\; \theta_{0,2} + \Delta\theta_2,\; \alpha_2)\]

That is:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Winding number \(N_i\) is invariant} --- the particle type
  does not change
\item
  \textbf{Translational phase \(\alpha_i\) is invariant} --- velocity
  (momentum) is conserved
\item
  \textbf{Only the central phase \(\theta_{0,i}\) changes} --- displaced
  by the phase shift \(\Delta\theta_i\)
\end{enumerate}

\textbf{Corollary 8.1.} All information about a soliton collision is
concentrated in the phase shifts \(\Delta\theta_i\). The phase shifts
are computable from the incident parameters {[}12{]}:

\[\Delta\theta_1 = -\Delta\theta_2 = f(N_1, N_2, \alpha_1 - \alpha_2)\]

That is, the collision depends only on the relative translational phase
\(\alpha_1 - \alpha_2\).

\subsubsection{8.7 Reduction from Continuous Fields to Parameter
Representation}\label{reduction-from-continuous-fields-to-parameter-representation}

Summarizing the above, the solution space of the sine-Gordon equation is
hierarchically structured as follows.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.4286}}
  >{\centering\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.2857}}
  >{\centering\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.2857}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Description level
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Degrees of freedom
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Information content
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Continuous field \(\phi(x, t)\) & Infinite-dimensional & Real value at
each spacetime point \\
\(n\)-soliton solution & \(3n\)-dimensional & Each soliton
\((N_i, \theta_{0,i}, \alpha_i)\) \\
Post-collision change & \(n\)-dimensional & Phase shifts
\(\Delta\theta_i\) only \\
\end{longtable}
}

\textbf{Proposition 8.4 (Finite-dimensionality of the soliton sector).}
The sector of the solution space of the sine-Gordon equation containing
\(n\) solitons is described as a \(3n\)-dimensional finite-dimensional
manifold (moduli space) \(\mathcal{M}_n\) {[}10, 22{]}. The infinite
degrees of freedom of the continuous field are \textbf{exactly} reduced
to a finite number of parameters in the soliton sector.

\emph{Proof.} In the inverse scattering method, the \(n\)-soliton sector
is characterized by \(n\) discrete eigenvalues \(\zeta_i\) and
associated norming constants \(c_i\) {[}12, 13{]}. Each eigenvalue
determines the winding number \(N_i\) and velocity \(v_i\) (=
\(\sin\alpha_i\)), while the norming constant determines the initial
position \(x_{0,i}\) (= \(\theta_{0,i}\)). Excluding the radiation
component (continuous spectrum), the degrees of freedom of the soliton
sector are exactly \(3n\). \(\square\)

This reduction is not an approximation. In the soliton sector, the
infinite-dimensional partial differential equation is \textbf{exactly}
reduced to a finite-dimensional system of ordinary differential
equations.

\subsubsection{8.8 Relation to Rectangular
Waves}\label{relation-to-rectangular-waves}

We re-examine the shape of the kink solution.

\[\phi_K(x) = 4\arctan(e^{x/\ell}) = 2\pi \cdot \frac{1}{1 + e^{-x/\ell}}\]

The right-hand side is the logistic function (sigmoid function), which
converges to a \textbf{step function} (half-period of a rectangular
wave) in the limit \(\ell \to 0\).

\[\lim_{\ell \to 0} \phi_K(x) = \begin{cases} 0 & (x < 0) \\ 2\pi & (x > 0) \end{cases}\]

\textbf{Proposition 8.5 (Rectangular-wave limit).} In the limit
\(\sigma = \ell \to 0\) of the spread parameter (i.e.,
\(\alpha \to \pm\pi/2\), the speed-of-light limit), the kink solution
converges to a rectangular wave (step function). Conversely, a kink with
finite width \(\sigma > 0\) can be understood as a \textbf{smoothed}
rectangular wave.

\emph{Proof.} \(\phi_K(x) = 2\pi/(1 + e^{-x/\ell})\) is a logistic
function, and it converges pointwise to the Heaviside step function
\(2\pi \cdot H(x)\) as \(\ell \to 0\). \(\square\)

\textbf{Corollary 8.2.} A soliton can be interpreted as a finite-mode
approximation of a rectangular wave. The continuous \(\tanh\)-type shape
is merely a smoothed version of a discrete step function. The spread
parameter \(\sigma\) controls the degree of smoothing.

From this perspective, the parameter representation of solitons is
reinterpreted as follows.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.2917}}
  >{\centering\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.4583}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Meaning in continuous field
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Meaning in rectangular wave (discrete)
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\(N = \pm 1\) & Winding number & Direction of step
(ascending/descending) \\
\(A = 2\pi\) & Total phase change & Height of step \\
\(\theta_0\) & Position of soliton center & Position of step edge \\
\(\alpha\) & Phase angle of velocity & Direction of edge motion \\
\(\sigma\) & Width of smoothing & \textbf{Coincides with rectangular
wave at \(\sigma \to 0\)} \\
\end{longtable}
}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{9. Preservation of Properties in the Rectangular-Wave
Limit}\label{preservation-of-properties-in-the-rectangular-wave-limit}

\subsubsection{9.1 Purpose}\label{purpose-1}

The properties of the sine-Gordon equation described in §1--§7 have been
proved for the continuous field \(\phi(x, t)\). As shown in §8.8,
soliton solutions converge to rectangular waves (step functions) in the
limit \(\sigma \to 0\) of the spread parameter.

In this section, we systematically verify for each property in §1--§7
that (a) it holds for soliton solutions (this is trivial since they are
exact solutions), and (b) it is preserved in the rectangular-wave limit
\(\sigma \to 0\).

If all properties are preserved in the rectangular-wave limit, then the
rectangular-wave description is not a ``convenient approximation'' but
an \textbf{exact limit that completely inherits} the structure of
solitons.

\subsubsection{9.2 Framework of
Verification}\label{framework-of-verification}

Each property is verified in three stages.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Validity for soliton solutions}: Does it satisfy the
  sine-Gordon equation as an exact solution?
\item
  \textbf{Analysis of \(\sigma\)-dependence}: Does the property depend
  on the spread parameter \(\sigma\)?
\item
  \textbf{Existence of the rectangular-wave limit}: Is the property
  preserved or does it diverge as \(\sigma \to 0\)?
\end{enumerate}

\subsubsection{9.3 Definition and Conservation of Winding Number (§2.3 →
Rectangular
Wave)}\label{definition-and-conservation-of-winding-number-2.3-rectangular-wave}

\textbf{Property from §2.3:} The winding number
\(N = [\phi(+\infty) - \phi(-\infty)] / 2\pi\) is conserved under time
evolution.

\textbf{Validity for soliton solutions:} The kink solution gives
\(\phi(-\infty) = 0\), \(\phi(+\infty) = 2\pi\), yielding \(N = +1\).
Since this is an exact solution of the sine-Gordon equation,
conservation of \(N\) is trivial. \(\checkmark\)

\textbf{\(\sigma\)-dependence:} The definition
\(N = [\phi(+\infty) - \phi(-\infty)] / 2\pi\) depends \textbf{only on
boundary values} and is entirely independent of the internal shape of
\(\phi\) (and hence of \(\sigma\)).

\textbf{Proposition 9.1 (\(\sigma\)-independence of winding number).}
The winding number \(N\) does not depend on the spread parameter
\(\sigma\). It retains the same integer value in the rectangular-wave
limit \(\sigma \to 0\).

\emph{Proof.} For any \(\sigma > 0\), \(\phi_K^\sigma(\pm\infty)\) is
fixed at the vacuum values \(0, 2\pi\). In the limit \(\sigma \to 0\),
\(\phi_K^\sigma(x) \to 2\pi \cdot H(x)\) pointwise, and since
\(H(-\infty) = 0\), \(H(+\infty) = 1\), we have
\(N = (2\pi \cdot 1 - 2\pi \cdot 0)/2\pi = 1\), unchanged. \(\square\)

\textbf{Winding number for rectangular waves:} For the rectangular wave
\(\phi(x) = 2\pi H(x - x_0)\), \(N = +1\). If the step is ascending,
\(N = +1\); if descending, \(N = -1\). The winding number is precisely
the sign of the step. \(\checkmark\)

\subsubsection{9.4 Conservation Law of Winding Number (Proposition 2.1 →
Rectangular
Wave)}\label{conservation-law-of-winding-number-proposition-2.1-rectangular-wave}

\textbf{Property from §2.3:} \(N\) is conserved under time evolution.
Creation and annihilation are possible only as kink-antikink pairs.

\textbf{\(\sigma\)-dependence:} The proof of the conservation law (§2.3)
relies solely on the fact that ``boundary values are fixed at vacuum
values and cannot change by an integer multiple of \(2\pi\) under
continuous time evolution.'' This argument is independent of \(\sigma\).

\textbf{Conservation for rectangular waves:} The boundary values of a
rectangular wave are \(0\) and \(2\pi\), taking only discrete values.
Discrete values cannot change under continuous deformation. Therefore,
conservation of the winding number for rectangular waves is \textbf{even
more trivially} satisfied than for continuous fields.

\textbf{Proposition 9.2.} The conservation law of the winding number
holds exactly in the rectangular-wave limit. Moreover, since \(\phi\)
itself takes only discrete values (\(0\) or \(2\pi\)) for rectangular
waves, conservation is guaranteed not only topologically but also by the
\textbf{discreteness of values}. \(\checkmark\)

\subsubsection{9.5 Existence of Kink and Antikink Solutions (§2.1, §2.2
→ Rectangular
Wave)}\label{existence-of-kink-and-antikink-solutions-2.1-2.2-rectangular-wave}

\textbf{Property from §2.1--2.2:} Localized solutions with winding
number \(\pm 1\) exist and propagate with velocity \(v\).

\textbf{Validity for soliton solutions:} The kink
\(\phi_K = 4\arctan(\exp((x-vt)/\sigma))\) is an exact solution.
\(\checkmark\)

\textbf{Rectangular-wave limit:} As \(\sigma \to 0\),
\(\phi_K \to 2\pi \cdot H(x - vt)\). This is a step function moving with
velocity \(v\), preserving localization and propagation.

\textbf{Proposition 9.3 (Existence of rectangular-wave kink).} The
rectangular-wave kink \(\phi(x, t) = 2\pi \cdot H(x - vt)\) has the
following properties. 1. Winding number \(N = +1\) 2. Moves with
velocity \(v\) 3. Localized at a single spatial point (\(x = vt\)) 4.
Holds as a \textbf{distributional solution} of the sine-Gordon equation

\emph{Proof.} (1)--(3) are immediate from the definition. For (4): the
distributional derivatives of \(\phi = 2\pi H(x - vt)\) are
\(\phi_x = 2\pi\delta(x-vt)\), \(\phi_{xx} = 2\pi\delta'(x-vt)\),
\(\phi_{tt} = 2\pi v^2\delta'(x-vt)\), and
\(\sin(\phi) = \sin(2\pi H(x-vt)) = 0\) (since \(\phi = 0\) or \(2\pi\)
for \(x \neq vt\), and \(\sin = 0\) in both cases). The wave-equation
part \(\phi_{tt} - \phi_{xx} = 2\pi(v^2-1)\delta'(x-vt)\) vanishes only
for \(v = \pm 1\) (speed of light). For \(v \neq 1\), the rectangular
wave is not a classical solution, and smoothing with finite width
\(\sigma > 0\) is required. \(\square\)

\textbf{Note.} The fact that the rectangular wave is not an exact
solution for \(v \neq 1\) is consistent with the relation
\(\sigma = \cos\alpha = \sqrt{1-v^2}\) from §8.3. If \(v < 1\) then
\(\sigma > 0\), and the soliton has finite width. A rectangular wave
(\(\sigma = 0\)) corresponds only to \(v = 1\) (speed of light). The
fact that subluminal particles have finite ``extent'' is qualitatively
consistent with the spread of wave packets in quantum mechanics.

\subsubsection{9.6 Breather Solution (§2.4 → Rectangular
Wave)}\label{breather-solution-2.4-rectangular-wave}

\textbf{Property from §2.4:} A breather exists as a bound state of a
kink-antikink pair.

\textbf{Rectangular-wave limit:} The breather is an oscillatory solution
with winding number \(N = 0\). In the rectangular-wave limit, it
corresponds to a \textbf{rectangular pulse} oscillating between \(0\)
and \(2\pi\).

\textbf{Proposition 9.4.} The rectangular-wave limit of the breather is
a spatially localized rectangular pulse oscillating between the two
states of presence (\(\phi = 2\pi\)) and absence (\(\phi = 0\)). The
mass \(M_B = 16\sqrt{1-\omega^2}\) depends on \(\omega\) and is not
directly dependent on \(\sigma\). \(\checkmark\)

\subsubsection{9.7 Soliton Collisions and Phase Shift (§3 → Rectangular
Wave)}\label{soliton-collisions-and-phase-shift-3-rectangular-wave}

\textbf{Property from §3:} After collision, (i) shape preservation, (ii)
phase shift, (iii) conservation of winding number.

This is the most important property, and we verify each item
individually.

\textbf{(i) Shape preservation:}

\textbf{Soliton solutions:} Each soliton after the collision has the
same shape (same \(\sigma\)) as before {[}12{]}. \(\checkmark\)

\textbf{Rectangular-wave limit:} A rectangular wave has \(\sigma = 0\),
and the only shape parameter is ``step height \(2\pi\).'' If
\(\sigma = 0\) is preserved before and after the collision, shape
preservation holds automatically. Since \(\sigma\) is a conserved
quantity in soliton collisions (Proposition 8.3: \(\alpha_i\) invariant
\(\Rightarrow\) \(\sigma_i = \cos\alpha_i\) invariant), \(\sigma = 0\)
is also preserved. \(\checkmark\)

\textbf{(ii) Phase shift:}

\textbf{Soliton solutions:} The phase shift after collision is
\(\Delta\theta = f(N_1, N_2, \alpha_1 - \alpha_2)\) {[}12{]}.
\(\checkmark\)

\textbf{Rectangular-wave limit:} The phase-shift formula depends only on
\(\alpha_i\) (translational phase) and not on \(\sigma_i\) (spread) (see
§8.6 Corollary 8.1). Therefore, the phase-shift value does not change
even as \(\sigma \to 0\).

\textbf{Proposition 9.5 (\(\sigma\)-independence of phase shift).} The
phase shift \(\Delta\theta\) in a soliton collision does not depend on
the spread parameters \(\sigma_i\) of the individual solitons. In the
rectangular-wave limit \(\sigma \to 0\), the phase shift takes the same
value as for solitons.

\emph{Proof.} In the inverse scattering method, the phase shift is
computed solely from the discrete eigenvalues \(\zeta_i\) of the
scattering data {[}12, 13{]}. \(\zeta_i\) is determined by the velocity
\(v_i = \sin\alpha_i\) and winding number \(N_i\) of the soliton,
independent of the norming constants (position information) and the
radiation component. The soliton width \(\sigma_i\) is related to the
norming constants but does not contribute to the phase shift.
\(\square\)

\textbf{(iii) Conservation of winding number:} Already shown in §9.4.
\(\checkmark\)

\subsubsection{9.8 Complete Integrability and Conserved Quantities (§4 →
Rectangular
Wave)}\label{complete-integrability-and-conserved-quantities-4-rectangular-wave}

\textbf{Property from §4:} Conservation of energy, momentum, and winding
number.

\textbf{Energy:}

The energy of a soliton is
\(E = 8/\sigma = 8/\cos\alpha = 8/\sqrt{1-v^2}\). As \(\sigma \to 0\),
the energy diverges.

\textbf{Proposition 9.6 (\(\sigma\)-dependence of energy).} The energy
of a soliton depends on \(\sigma\), diverging as \(E \to \infty\) when
\(\sigma \to 0\). This means that the rectangular-wave limit has
infinite energy.

\textbf{Proposition 9.6a (Limitations of the theory).} The sine-Gordon
soliton theory is based on the following implicit assumptions.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Fixed starting point}: The initial value of the field is fixed
  at the vacuum value \(\phi(-\infty) = 0\) (§2.1).
\item
  \textbf{Periodicity of the potential}: \(V(\phi) = 1-\cos\phi\) has
  period \(2\pi\), and the target space is effectively \(S^1\). The size
  of one ``period'' of the potential (\(2\pi\)) is fixed by the theory
  and has no freedom to be changed.
\item
  \textbf{Forcing the terminus to a vacuum value}: The requirement of
  finite energy on infinite space \((-\infty, +\infty)\) forces
  \(\phi(+\infty) = 2n\pi\) (\(n \in \mathbb{Z}\)). This is because
  \(V(2n\pi) = 0\) (potential minimum), while \(\phi = (2n+1)\pi\) gives
  \(V = 2\) (potential maximum), and the energy diverges on infinite
  space, excluding such configurations.
\item
  \textbf{Exclusion of fractional winding numbers}: As a consequence of
  the above, the winding number \(N\) is always an integer. Half-integer
  winding numbers (\(\phi(+\infty) = (2n+1)\pi\)) are automatically
  excluded by the finite-energy requirement.
\item
  \textbf{Absence of boundary reflection}: Since the space is infinite
  or closed (\(S^1\)), no physical boundaries exist, and boundary
  reflection of solitons does not occur.
\item
  \textbf{Perfectly elastic collisions and absence of interaction}: The
  theory is a completely integrable system (§4) with infinitely many
  conserved quantities. As a consequence of this excessive constraint,
  soliton collisions are described as perfectly elastic collisions, in
  which the velocity, shape, and energy of each soliton are
  \textbf{individually} conserved before and after the collision (§3.3).
  To avoid violating momentum conservation, only the position (phase
  shift \(\Delta x\)) of each soliton changes, and no exchange of
  velocities, deformation of shapes, or dissipation of energy occurs.
  This effectively means that solitons behave as \textbf{free particles
  that do not interact}. In the case of identical particles (e.g.,
  kink-kink collision), it is in principle indistinguishable whether
  they ``passed through each other'' or ``bounced off.''
\end{enumerate}

\emph{Consequence.} This theory can be consistently applied only in the
following two cases.

\begin{itemize}
\tightlist
\item
  \textbf{Infinite space} \((-\infty, +\infty)\): The terminus is at
  infinity and is never reached. The energy per kink is \(E = 8\) (at
  rest), which is finite.
\item
  \textbf{Closed curve} \(S^1\) (circumference \(L\)): Periodic boundary
  conditions \(\phi(x+L) = \phi(x) + 2\pi N\). No boundary exists.
\end{itemize}

\textbf{Open strings} (Dirichlet/Neumann boundary conditions on a finite
interval \([0, L]\)) fall outside the scope of this theory. The reason
is that a finite interval \([0, L]\) is a contractible space
(\(\pi_1([0,L]) = 0\)), so the winding number is not defined as a
topological invariant, and the topological stability of solitons is not
guaranteed. Furthermore, on a finite interval, \(\phi(L) = (2n+1)\pi\)
(half-integer winding number, potential maximum) is energetically
admissible, so the restriction to integer winding numbers breaks down.

\textbf{Self-cancellation structure of energy:} The energy of each
\(2\pi\) rotation (one kink) is \(E = 8\) (at rest) and is
self-contained. This is because the potential \(V(\phi) = 1-\cos\phi\)
returns from \(0\) to \(0\) over one period. A kink-antikink pair
(\(4\pi\) rotation, winding number \(N = 0\)) can annihilate to return
the energy to zero. The only observable persistent energy is the
contribution \(8|N|\) from the \(|N|\) surplus kinks that cannot
pair-annihilate.

\textbf{Momentum and winding number:} Momentum \(P = -Ev\) has the same
structure. The winding number is \(\sigma\)-independent as shown in
§9.3. \(\checkmark\)

\subsubsection{9.9 Extension to Higher Dimensions (§5 → Rectangular
Wave)}\label{extension-to-higher-dimensions-5-rectangular-wave}

\textbf{Property from §5:} By Derrick's theorem, no stable localized
solutions exist in 3+1-dimensional infinite space.

\textbf{Impact on the rectangular-wave limit:} The premise of Derrick's
theorem is the existence of \textbf{finite-energy solutions on infinite
space} {[}17{]}. On a closed curve \(S^1\) (circumference \(L\)), the
premises of the theorem are violated for the following two reasons.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Space is closed}: The range of \(\lambda\) in the scale
  transformation \(\phi(x) \to \phi(\lambda x)\) is restricted
\item
  \textbf{Topological protection}: The winding number
  \(N \in \pi_1(S^1) = \mathbb{Z}\) is protected as a topological
  invariant
\end{enumerate}

\textbf{Proposition 9.7.} On a closed curve \(S^1\) (circumference
\(L\)), localized solutions of any width, including rectangular waves
(\(\sigma = 0\)), are topologically stable. Derrick's theorem does not
apply to closed spaces. \(\checkmark\)

\subsubsection{9.10 Summary of Verification
Results}\label{summary-of-verification-results}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1132}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.0755}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1698}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.3019}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.2264}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1132}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Property
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Section
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Soliton
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\sigma\)-dependence
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Rectangular-wave limit
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Remarks
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Winding number definition & §2.3 & \(\checkmark\) & \textbf{Independent}
& \(\checkmark\) & Boundary values only \\
Winding number conservation & §2.3 & \(\checkmark\) &
\textbf{Independent} & \(\checkmark\) & Topological \\
Kink/antikink existence & §2.1--2 & \(\checkmark\) & Shape only &
\(\checkmark\) & Distributional solution \\
Breather existence & §2.4 & \(\checkmark\) & Shape only & \(\checkmark\)
& Rectangular pulse \\
Shape preservation after collision & §3.1--2 & \(\checkmark\) &
\textbf{Independent} & \(\checkmark\) & \(\sigma\) conserved \\
Phase shift after collision & §3.3 & \(\checkmark\) &
\textbf{Independent} & \(\checkmark\) & \(\alpha\) only \\
Winding number conservation (collision) & §3.3 & \(\checkmark\) &
\textbf{Independent} & \(\checkmark\) & Topological \\
Energy conservation & §4.2 & \(\checkmark\) & Dependent &
\(\checkmark\)* & *Self-contained per \(2\pi\) rotation \\
Momentum conservation & §4.2 & \(\checkmark\) & Dependent &
\(\checkmark\)* & *Same as above \\
Derrick avoidance & §5.1--2 & --- & --- & \(\checkmark\) & Closed space
\(S^1\) \\
Parameter representation \((N, \theta_0, \alpha)\) & §8 & \(\checkmark\)
& \textbf{Independent} & \(\checkmark\) & \(\sigma\) is subordinate \\
\end{longtable}
}

\textbf{Theorem 9.1 (Structural preservation in the rectangular-wave
limit).} The following structural properties of soliton solutions of the
sine-Gordon equation are all preserved in the rectangular-wave limit
\(\sigma \to 0\).

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Definition and conservation of winding number} (topological
  property: \(\sigma\)-independent)
\item
  \textbf{Shape preservation and phase shift after collision} (property
  of scattering data: \(\sigma\)-independent)
\item
  \textbf{Finite-parameter representation} \((N, \theta_0, \alpha)\)
  (structure of moduli space: \(\sigma\)-independent)
\item
  \textbf{Finiteness of energy and momentum} (by the self-cancellation
  structure of each \(2\pi\) rotation. Proposition 9.6a)
\end{enumerate}

\emph{Proof.} (1) follows from Propositions 9.1--9.2, (2) from
Proposition 9.5, (3) from Proposition 8.4 and the subordination
\(\sigma = \cos\alpha\), (4) from the energy self-cancellation structure
in Proposition 9.6a. \(\square\)

\textbf{Corollary 9.1.} The rectangular-wave description is not a
``crude approximation'' of the soliton. It is an \textbf{exact limit
that completely inherits} the topological and scattering structures of
the soliton. The only information lost is the spread parameter
\(\sigma\) (details of the internal shape).

\textbf{Corollary 9.2 (Scope of applicability).} The validity of this
theorem depends on the implicit assumptions of the theory made explicit
in Proposition 9.6a --- the fixed starting point \(\phi = 0\), the
forcing of the terminus to a vacuum value (\(2n\pi\)), and integer
winding numbers. These assumptions hold only on infinite space
\((-\infty,+\infty)\) or on a closed curve \(S^1\). Extension to open
strings (boundary conditions on a finite interval) requires admitting
half-integer winding numbers and a theory of boundary reflection
(Ghoshal-Zamolodchikov {[}23{]}), which is beyond the scope of this
paper.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{10. Conclusion}\label{conclusion}

In this paper, we surveyed the mathematical structure of the sine-Gordon
equation and demonstrated the following.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Soliton solutions (kink, antikink, breather) are \textbf{exactly}
  characterized by a finite number of parameters
  \((N, \theta_0, \alpha)\) (§8).
\item
  All structural properties of solitons --- conservation of winding
  number, shape preservation and phase shift in collisions,
  finite-parameter representation --- are preserved in the
  rectangular-wave limit \(\sigma \to 0\) (§9).
\item
  The finiteness of energy is based on the structure in which the energy
  of each \(2\pi\) rotation is self-contained (the potential
  \(V(\phi) = 1-\cos\phi\) returns from \(0\) to \(0\) over one period).
  Kink-antikink pairs (\(4\pi\) rotation) can pair-annihilate, and
  persistent energy consists only of the contribution from surplus kinks
  that cannot pair-annihilate.
\item
  Therefore, the transition from solitons to rectangular waves entails
  no loss of information. Among the infinite degrees of freedom of the
  continuous field, the physically meaningful information is
  concentrated in the finite number of parameters
  \((N, \theta_0, \alpha)\), and this concentration holds regardless of
  the soliton shape.
\end{enumerate}

\textbf{Limitations of applicability:} The above conclusions hold under
the implicit assumptions of the theory (Proposition 9.6a).

\begin{itemize}
\tightlist
\item
  \textbf{Spatial constraints}: The phase at the starting point is fixed
  at the vacuum value \(\phi = 0\), and the phase at the terminus is
  forced to a vacuum value \(\phi = 2n\pi\) (winding number \(N\) is
  integer only). No boundary reflection exists. These conditions are
  satisfied only on infinite space \((-\infty, +\infty)\) or a closed
  curve \(S^1\). Extension to open strings (boundary conditions on a
  finite interval) requires admitting half-integer winding numbers
  (\(\phi = (2n+1)\pi\), potential maximum) and handling soliton
  reflection at boundaries, which is beyond the scope of this paper.
\item
  \textbf{Collision constraints}: This theory is a completely integrable
  system, and soliton collisions are described as perfectly elastic
  collisions. To avoid violating momentum conservation, the velocity,
  shape, and energy of each soliton are individually conserved before
  and after the collision, and only the position (phase shift
  \(\Delta x\)) changes. This effectively means that solitons behave as
  free particles that do not interact, and dissipation of energy,
  exchange of velocities, and inelastic channels (pair-annihilation →
  radiation) do not occur within the classical theory.
\end{itemize}

The rectangular-wave description is not a ``crude approximation'' of the
soliton but an exact limit that completely inherits the topological and
scattering structures. The fact that solutions of nonlinear wave
equations are reduced to a finite number of discrete parameters reveals
a deep correspondence between the theory of continuous fields and
discrete structures.

An alternative model that overcomes the above limitations --- in
particular, the inability to handle particles of different masses and
the absence of velocity redistribution after collisions --- is presented
in §11.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{11. Perfectly Elastic Collision Model at Arbitrary Phases in
a Perfect
Fluid}\label{perfectly-elastic-collision-model-at-arbitrary-phases-in-a-perfect-fluid}

In §9--10, we identified the limitations of the sine-Gordon soliton
theory. In particular, (i) all solitons have the same mass, and (ii) no
velocity redistribution occurs after collisions (transmissive
collisions), which are insufficient for describing physical elastic
collisions.

In this section, we formulate an alternative model without these
constraints: \textbf{perfectly elastic collisions at arbitrary phases in
a perfect fluid with different specific gravities (masses)}, within the
framework of wave equations.

This model is based on the wave equation for longitudinal waves (sound
waves) in a perfect fluid. Waves in a perfect fluid are inherently
longitudinal, and the propagation velocity depends on the density
(specific gravity) of the medium (\(c = \sqrt{K/\rho}\)). The collision
of two waves with different specific gravities is completely described
by momentum conservation and energy conservation. Below, we formulate
this physics in terms of a spring-mass system, which provides the most
transparent representation.

\subsubsection{11.1 Model Construction}\label{model-construction}

Two perfect springs (zero dissipation) with spring constant \(k\) and
natural length \(l\) are connected in series, with both ends fixed to
walls separated by a distance \(2l\). A point mass \(M\) is placed at
the junction of the two springs.

\[\text{Wall}—[\,k,\; l\,]—M—[\,k,\; l\,]—\text{Wall}\]

Letting \(x\) denote the displacement from the equilibrium position
(center), the restoring forces from the left spring \(-kx\) and the
right spring \(-kx\) combine to give the equation of motion

\[M\ddot{x} + 2kx = 0 \tag{W1}\]

This is simple harmonic motion (longitudinal wave) with angular
frequency \(\omega = \sqrt{2k/M}\). The general solution is

\[x(t) = A\cos(\omega t + \phi_0) \tag{W2}\]

where \(A\) is the amplitude and \(\phi_0\) is the initial phase.

\subsubsection{11.2 Two-Body Configuration and Definition of
Collision}\label{two-body-configuration-and-definition-of-collision}

We consider two independent simple harmonic oscillators with different
masses \(M_1, M_2\).

\[\ddot{x}_1 + \omega_1^2 x_1 = 0, \qquad \omega_1 = \sqrt{\frac{2k}{M_1}} \tag{W3}\]

\[\ddot{x}_2 + \omega_2^2 x_2 = 0, \qquad \omega_2 = \sqrt{\frac{2k}{M_2}} \tag{W4}\]

When \(M_1 \neq M_2\), \(\omega_1 \neq \omega_2\), and the two systems
oscillate independently. The difference in specific gravity of the
perfect fluid corresponds to this mass difference \(M_1 \neq M_2\).

\textbf{Definition of collision.} In this paper, a ``collision'' is
defined as a mathematical process in which the states
\((x_1, \dot{x}_1)\) and \((x_2, \dot{x}_2)\) of the two systems
interact via momentum conservation and energy conservation at a given
time \(t = t_c\), instantaneously transitioning to new states
\((x_1, \dot{x}_1')\) and \((x_2, \dot{x}_2')\). Positions \(x_i\) do
not change due to the collision; only velocities \(v_i = \dot{x}_i\)
change according to (W7)--(W8).

\textbf{Remark.} In this model, a collision is not a geometric
description of physical contact but an abstraction: an ``instantaneous
state transition in which the states of two oscillatory systems are
coupled via conservation laws.'' It replaces the role of the physical
contact surface in longitudinal wave collisions in a perfect fluid with
a state transformation via conservation laws. The collision time \(t_c\)
is an input parameter given externally and is not determined from within
the model. This allows collisions at arbitrary phases \(\phi_1, \phi_2\)
to be treated in a unified manner.

\subsubsection{11.3 Perfectly Elastic Collision at Arbitrary
Phases}\label{perfectly-elastic-collision-at-arbitrary-phases}

\textbf{Pre-collision state:} The state of each system at time \(t_c\)
is expressed as follows.

\[x_{1,c} = A_1\cos\phi_1, \qquad v_1 = -A_1\omega_1\sin\phi_1 \tag{W5}\]

\[x_{2,c} = A_2\cos\phi_2, \qquad v_2 = -A_2\omega_2\sin\phi_2 \tag{W6}\]

Here \(\phi_i = \omega_i t_c + \phi_{0,i}\) is the phase of each system
at the collision instant, and \(A_i\) is the amplitude. The sign of the
velocity follows from the natural differentiation of (W3)(W4).

\textbf{Conditions for perfectly elastic collision (momentum
conservation + energy conservation):}

\[M_1 v_1 + M_2 v_2 = M_1 v_1' + M_2 v_2' \tag{W7}\]

\[\frac{1}{2}M_1 v_1^2 + \frac{1}{2}M_2 v_2^2 = \frac{1}{2}M_1 v_1'^2 + \frac{1}{2}M_2 v_2'^2 \tag{W8}\]

These two conditions uniquely determine the post-collision velocities.

\textbf{Theorem 11.1 (Elastic collision formula at arbitrary phases).}
The post-collision velocities of a perfectly elastic collision between
masses \(M_1, M_2\) at phases \(\phi_1, \phi_2\) are given by:

\[v_1' = \frac{(M_1 - M_2)\,v_1 + 2M_2\,v_2}{M_1 + M_2} \tag{W9}\]

\[v_2' = \frac{(M_2 - M_1)\,v_2 + 2M_1\,v_1}{M_1 + M_2} \tag{W10}\]

\emph{Proof.} Obtained directly by solving the system of equations (W7)
and (W8). \(\square\)

\subsubsection{11.4 Post-Collision Oscillation
State}\label{post-collision-oscillation-state}

The collision is instantaneous, and positions do not change. After the
collision, each mass resumes oscillation in its original spring system
with the collision-time position \(x_{i,c}\) and the new velocity
\(v_i'\) as initial conditions.

\[x_1(t) = x_{1,c}\cos(\omega_1\tau) + \frac{v_1'}{\omega_1}\sin(\omega_1\tau) \qquad (\tau = t - t_c) \tag{W11}\]

\[x_2(t) = x_{2,c}\cos(\omega_2\tau) + \frac{v_2'}{\omega_2}\sin(\omega_2\tau) \tag{W12}\]

\textbf{Post-collision amplitude and phase:}

\[A_i' = \sqrt{x_{i,c}^2 + \left(\frac{v_i'}{\omega_i}\right)^2} \tag{W13}\]

\[\phi_i' = \arctan\!\left(\frac{-v_i'}{\omega_i\, x_{i,c}}\right) \tag{W14}\]

The angular frequency \(\omega_i\) is determined solely by the spring
constant and mass, and is not changed by the collision. What changes are
only the amplitude \(A_i\) and the phase \(\phi_i\).

\subsubsection{11.5 Proof of Energy
Conservation}\label{proof-of-energy-conservation}

\textbf{Proposition 11.1.} In a perfectly elastic collision at arbitrary
phases, the total energy of the system is conserved.

\emph{Proof.} The total energy of each system is the sum of the spring's
potential energy and kinetic energy.

\[E_i = \frac{1}{2}M_i\omega_i^2\,x_{i,c}^2 + \frac{1}{2}M_i\,v_i^2 = k\,x_{i,c}^2 + \frac{1}{2}M_i\,v_i^2\]

Since the collision is instantaneous, the potential energy
\(k\,x_{i,c}^2\) is unchanged before and after the collision. The
kinetic energy is conserved by the elastic collision condition (W8).
Therefore

\[E_1 + E_2 = E_1' + E_2' \qquad \square \tag{W15}\]

\subsubsection{11.6 Characteristics of Amplitude and Phase Changes by
Collision
Phase}\label{characteristics-of-amplitude-and-phase-changes-by-collision-phase}

From the elastic collision formulas (W9)--(W10) and the post-collision
amplitude/phase determination formulas (W19)(W14), the following
characteristics emerge depending on the collision-instant phase
\(\phi_i\).

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Collision phase
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Position \(x_{i,c}\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Velocity \(|v_i|\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Energy partition
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Collision effect
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\(\phi_i = \pi/2\) & \(0\) & \(A_i\omega_i\) (maximum) & All kinetic
energy & Velocity is fully redistributed; only amplitude \(A_i\)
changes \\
\(\phi_i = 0\) & \(A_i\) (maximum) & \(0\) & All potential energy & No
velocity exchange occurs; state is unchanged before and after \\
\(\phi_i = \pi/4\) & \(A_i/\sqrt{2}\) & \(A_i\omega_i/\sqrt{2}\) &
Equally partitioned & Partial velocity redistribution and phase shift
occur \\
\end{longtable}
}

\textbf{Remark.} The ``unchanged state'' at \(\phi_i = 0\) arises
because the right-hand sides of (W9)(W10) are determined solely by
\(v_i\), and \(v_i = 0\) yields \(v_i' = 0\) as the solution. This does
not mean that no collision occurs, but rather that the states with zero
velocity, upon being coupled via conservation laws, remain invariant. In
the general case \(\phi_1 \neq \phi_2\), a nontrivial state
transformation necessarily occurs as long as both velocities are not
simultaneously zero.

\subsubsection{11.7 Comparison with the sine-Gordon
Theory}\label{comparison-with-the-sine-gordon-theory}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Property
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
sine-Gordon (§1--10)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
This model (§11)
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Different masses & Impossible (all kinks have identical mass) &
\textbf{Possible} (\(M_1 \neq M_2\)) \\
Post-collision velocity redistribution & None (transmissive) &
\textbf{Present} (elastic collision formula) \\
Collision at arbitrary phases & Undefined & \textbf{Fully defined} \\
Closed-string assumption & Required (implicit) & \textbf{Not
required} \\
Integer winding number constraint & Required & \textbf{Not required} \\
Half-integer phase & Excluded (\(\phi = \pi\) inadmissible) &
\textbf{Admissible} \\
Wave equation & \(\phi_{tt} - \phi_{xx} + \sin\phi = 0\) &
\(\ddot{x}_i + \omega_i^2 x_i = 0\) \\
Hidden assumptions & 6 (Proposition 9.6a) & \textbf{None} (conservation
laws only) \\
Energy dissipation & Zero & Zero \\
Prerequisites of formulation & Momentum conservation + energy
conservation + topological constraints + integrability + closed space +
identical masses & \textbf{Momentum conservation + energy conservation
only} \\
\end{longtable}
}

\subsubsection{11.8 Physical
Interpretation}\label{physical-interpretation}

The physical correspondences of the parameters in this model are shown
below.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Model parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Physical correspondence
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mass \(M_i\) & Specific gravity (density) of the perfect fluid \\
Amplitude \(A_i\) & Wave amplitude (magnitude of energy) \\
Phase \(\phi_i\) & Wave phase \\
Angular frequency \(\omega_i = \sqrt{2k/M_i}\) & Natural frequency
(depends on specific gravity) \\
Collision (state transition) & Instantaneous interaction of waves via
conservation laws \\
\end{longtable}
}

The process in which longitudinal waves in a perfect fluid undergo
perfectly elastic collision is completely described by (W1)--(W15). The
only assumptions are the two conservation laws of momentum and energy;
no additional assumptions of topological constraints, integrability,
compactness of space, or integer winding numbers are required.

\subsubsection{11.9 Equivalence with the Rectangular-Wave
Limit}\label{equivalence-with-the-rectangular-wave-limit}

In §9, we showed that the solitons of the sine-Gordon equation preserve
their structure in the rectangular-wave limit. In this section, we prove
that for the model of §11 as well, the collision results remain
identical when the waveform changes from a sinusoidal (cosine) wave to a
rectangular wave.

\textbf{Introduction of the waveform parameter.} We define a family
\(x^\sigma(t)\) of oscillation waveforms controlled by the
transition-width parameter \(\sigma\) (\(0 < \sigma \leq 1\)).

\begin{itemize}
\tightlist
\item
  \(\sigma = 1\): Smooth sinusoidal (cosine) wave
  \(x^1(t) = A\cos(\omega t)\)
\item
  \(\sigma \to 0\): Rectangular wave
  \(x^0(t) = A\,\mathrm{sgn}(\cos(\omega t))\)
\end{itemize}

Intermediate \(\sigma\) controls the steepness of the transition region.
For all \(\sigma\), the amplitude is \(A\) and the period is
\(T = 2\pi/\omega\).

\textbf{Theorem 11.2 (Waveform independence of collision results).}
Given the collision-time positions \(x_{i,c}\) and total energies
\(E_i\), the post-collision velocities \(v_i'\), amplitudes \(A_i'\),
and phases \(\phi_i'\) do not depend on the waveform parameter
\(\sigma\).

\emph{Proof.} We show this in three stages.

\textbf{Stage 1: The collision-time velocity is uniquely determined by
energy and position.}

The total energy of the spring-mass system is conserved regardless of
the waveform.

\[E_i = k\,x_i^2(t) + \frac{1}{2}M_i\,\dot{x}_i^2(t) = k\,A_i^2 \tag{W16}\]

This is independent of the waveform. The spring's potential energy is a
function of position only, and the kinetic energy is the remainder.
Therefore, the velocity at the collision position \(x_{i,c}\) is

\[v_i^2 = \frac{2(E_i - k\,x_{i,c}^2)}{M_i} = \omega_i^2(A_i^2 - x_{i,c}^2) \tag{W17}\]

and is \textbf{uniquely} determined. This is independent of \(\sigma\).
Whether the wave is sinusoidal or rectangular, a mass passing through
the same position with the same energy has the same velocity.
\(\checkmark\)

\textbf{Stage 2: The elastic collision formula depends only on
velocities.}

The collision formulas (W9)--(W10) of Theorem 11.1 are algebraic
relations involving only \(M_1, M_2, v_1, v_2\), containing no waveform
information. Since Stage 1 showed that \(v_i\) is
\(\sigma\)-independent, \(v_i'\) is also \(\sigma\)-independent.
\(\checkmark\)

\textbf{Stage 3: Post-collision amplitudes and phases are also
\(\sigma\)-independent.}

The post-collision total energy is

\[E_i' = k\,x_{i,c}^2 + \frac{1}{2}M_i\,v_i'^2 \tag{W18}\]

and the new amplitude is

\[A_i' = \sqrt{\frac{E_i'}{k}} = \sqrt{x_{i,c}^2 + \frac{v_i'^2}{\omega_i^2}} \tag{W19}\]

Since \(x_{i,c}\), \(v_i'\), and \(\omega_i\) are all
\(\sigma\)-independent, \(A_i'\) is also \(\sigma\)-independent.

The initial phase \(\phi_i' = \arctan(-v_i'/(\omega_i\,x_{i,c}))\) is
similarly \(\sigma\)-independent. \(\square\)

\textbf{Corollary 11.1 (Exactness of the rectangular-wave limit).} The
results of perfectly elastic collision in this model are \textbf{exactly
identical} whether the oscillation is a smooth sinusoidal wave or a
rectangular wave. The only information lost is the detail of the
waveform (the shape of the transition region), while the physics of the
collision --- velocity redistribution, energy conservation, changes in
amplitude and phase --- does not depend on the waveform at all.

\textbf{Corollary 11.2.} This result reproduces, in a more general
framework, the structural preservation in the rectangular-wave limit
that was demonstrated for the sine-Gordon equation in §9. While the
proof of structural preservation in sine-Gordon required assumptions of
integrability and closed space, in this model the equivalence holds from
\textbf{the single condition of energy conservation} alone (equation
(W16)).

\subsubsection{11.10 Verification Summary of This
Model}\label{verification-summary-of-this-model}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1364}}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1818}}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1818}}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.3636}}
  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1364}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Property
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Sinusoidal wave
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Rectangular wave
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\(\sigma\)-dependence
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Remarks
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Collision-time velocity \(v_i\) & \(\checkmark\) & \(\checkmark\) &
\textbf{Independent} & By (W17) \\
Post-collision velocity \(v_i'\) & \(\checkmark\) & \(\checkmark\) &
\textbf{Independent} & (W9)--(W10) \\
Post-collision amplitude \(A_i'\) & \(\checkmark\) & \(\checkmark\) &
\textbf{Independent} & (W19) \\
Post-collision phase \(\phi_i'\) & \(\checkmark\) & \(\checkmark\) &
\textbf{Independent} & (W14) \\
Energy conservation & \(\checkmark\) & \(\checkmark\) &
\textbf{Independent} & (W15) \\
Momentum conservation & \(\checkmark\) & \(\checkmark\) &
\textbf{Independent} & (W7) \\
Different masses & \(\checkmark\) & \(\checkmark\) &
\textbf{Independent} & \(M_1 \neq M_2\) \\
Arbitrary phases & \(\checkmark\) & \(\checkmark\) &
\textbf{Independent} & \(\phi_1, \phi_2\) arbitrary \\
\end{longtable}
}

\textbf{Theorem 11.3 (Structural preservation of the perfectly elastic
collision model).} The process of perfectly elastic collision at
arbitrary phases \(\phi_1, \phi_2\) of longitudinal waves in a perfect
fluid with different specific gravities (masses \(M_1 \neq M_2\)) is
completely described by wave equations (W3)--(W4) and elastic collision
formulas (W9)--(W10), and all of the following properties are preserved
in the rectangular-wave limit \(\sigma \to 0\).

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Velocity redistribution} (elastic collision formula:
  \(\sigma\)-independent)
\item
  \textbf{Conservation of energy and momentum} ((W15) and (W7):
  \(\sigma\)-independent)
\item
  \textbf{Determination of amplitude and phase} ((W19) and (W14):
  \(\sigma\)-independent)
\end{enumerate}

\emph{Proof.} A direct consequence of Theorem 11.2. \(\square\)

The only assumptions of this entire formulation are the following two:

\begin{itemize}
\tightlist
\item
  \textbf{Momentum conservation}:
  \(M_1 v_1 + M_2 v_2 = M_1 v_1' + M_2 v_2'\)
\item
  \textbf{Energy conservation}:
  \(\frac{1}{2}M_1 v_1^2 + \frac{1}{2}M_2 v_2^2 = \frac{1}{2}M_1 v_1'^2 + \frac{1}{2}M_2 v_2'^2\)
\end{itemize}

No additional assumptions of topological constraints, integrability,
compactness of space, integer winding numbers, periodicity of potential,
or identical masses are required, and the equivalence with the
rectangular-wave limit follows automatically from energy conservation.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{References}\label{references}

{[}1{]} Frenkel, J. \& Kontorova, T. ``On the theory of plastic
deformation and twinning.'' \emph{Izv. Akad. Nauk SSSR, Ser. Fiz.} 1,
137--149 (1939).

{[}2{]} Scott, A.C., Chu, F.Y.F. \& McLaughlin, D.W. ``The Soliton: A
New Concept in Applied Science.'' \emph{Proc. IEEE} 61, 1443--1483
(1973).

{[}3{]} Rubinstein, J. ``Sine-Gordon equation.'' \emph{J. Math. Phys.}
11, 258--266 (1970).

{[}4{]} Rajaraman, R. \emph{Solitons and Instantons: An Introduction to
Solitons and Instantons in Quantum Field Theory.} North-Holland (1982).

{[}5{]} Bour, E. ``Théorie de la déformation des surfaces.'' \emph{J.
Éc. Imp. Polytech.} 22, Cahier 39, 1--148 (1862).

{[}6{]} Enneper, A. ``Über asymptotische Linien.'' \emph{Nachr. Königl.
Gesellsch. d.~Wiss. Göttingen} 1870, 493--510 (1870).

{[}7{]} Bianchi, L. ``Ricerche sulle superficie a curvatura costante e
sulle elicoidi.'' \emph{Ann. Sc. Norm. Super. Pisa} 2, 285--341 (1879).

{[}8{]} Skyrme, T.H.R. ``A non-linear field theory.'' \emph{Proc. R.
Soc. Lond. A} 260, 127--138 (1961).

{[}9{]} Perring, J.K. \& Skyrme, T.H.R. ``A model unified field
equation.'' \emph{Nucl. Phys.} 31, 550--555 (1962).

{[}10{]} Manton, N.S. \& Sutcliffe, P.M. \emph{Topological Solitons.}
Cambridge University Press (2004).

{[}11{]} Ablowitz, M.J., Kaup, D.J., Newell, A.C. \& Segur, H. ``Method
for solving the sine-Gordon equation.'' \emph{Phys. Rev.~Lett.} 30,
1262--1264 (1973).

{[}12{]} Ablowitz, M.J., Kaup, D.J., Newell, A.C. \& Segur, H. ``The
inverse scattering transform --- Fourier analysis for nonlinear
problems.'' \emph{Stud. Appl. Math.} 53, 249--315 (1974).

{[}13{]} Faddeev, L.D. \& Takhtajan, L.A. \emph{Hamiltonian Methods in
the Theory of Solitons.} Springer (1987).

{[}14{]} Zakharov, V.E. \& Shabat, A.B. ``Exact theory of
two-dimensional self-focusing and one-dimensional self-modulation of
waves in nonlinear media.'' \emph{Sov. Phys. JETP} 34, 62--69 (1972).

{[}15{]} Rogers, C. \& Schief, W.K. \emph{Bäcklund and Darboux
Transformations: Geometry and Modern Applications in Soliton Theory.}
Cambridge University Press (2002).

{[}16{]} Gibbon, J.D., James, I.N. \& Moroz, I.M. ``The sine-Gordon
equation as a model for a rapidly rotating baroclinic fluid.''
\emph{Proc. R. Soc. Lond. A} 367, 219--237 (1979).

{[}17{]} Derrick, G.H. ``Comments on nonlinear wave equations as models
for elementary particles.'' \emph{J. Math. Phys.} 5, 1252--1254 (1964).

{[}18{]} Manton, N.S. ``Geometry of Skyrmions.'' \emph{Commun. Math.
Phys.} 111, 469--478 (1987).

{[}19{]} Barone, A. \& Paternò, G. \emph{Physics and Applications of the
Josephson Effect.} Wiley (1982).

{[}20{]} Coleman, S. ``Quantum sine-Gordon equation as the massive
Thirring model.'' \emph{Phys. Rev.~D} 11, 2088--2097 (1975).

{[}21{]} Mandelstam, S. ``Soliton operators for the quantized
sine-Gordon equation.'' \emph{Phys. Rev.~D} 11, 3026--3030 (1975).

{[}22{]} Manton, N.S. ``A remark on the scattering of BPS monopoles.''
\emph{Phys. Lett. B} 110, 54--56 (1982).

{[}23{]} Ghoshal, S. \& Zamolodchikov, A.B. ``Boundary S matrix and
boundary state in two-dimensional integrable quantum field theory.''
\emph{Int. J. Mod. Phys. A} 9, 3841--3885 (1994).

\end{document}
